model4you reproducing: Individual treatment effect prediction for amyotrophic lateral sclerosis patients

### 2018-01-10 pkg/model4you/inst/reproducing_papers/2017_individual_treatment_effect_als_smmr.Rmd
trying to get varimp to work
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1933 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: b62ce9ea3101aa7f0c075f5a02dbfe3b24494af4

## Variable importance
```{r}
vi_alsfrs <- varimp(frst_alsfrs, 
                    risk = function(x, ...) -objfun(x, sum = TRUE, ...), 
                    nperm = 1)
var <- names(vi_alsfrs)
vi_alsfrs_d <- data.frame(variable = factor(var, levels = var[order(vi_alsfrs)]), 
                          VI = vi_alsfrs)

>>>>

## Variable importance
```{r}
set.seed(123)
vi_alsfrs <- varimp(frst_alsfrs, 
                    risk = function(x, ...) -objfun(x, sum = TRUE, ...), 
                    nperm = 1)
var <- names(vi_alsfrs)
vi_alsfrs_d <- data.frame(variable = factor(var, levels = var[order(vi_alsfrs)]), 
                          VI = vi_alsfrs)
